---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# shinymisc: Miscellaneous shiny apps built as part of debugging/exploration 

This repository holds code for apps I built mainly as part of my debugging and exploration process. They are shared here for educational purposes only. If you find them useful, please cite as necessary. If you would like to build these apps further, please fork the repository and suggest changes so I can review.

## Installation 



```{r, eval=FALSE}

devtools::install_github("Nelson-Gon/shinymisc")

```

## Loading the package 


```{r}
library(shinymisc)
```

## Exploring included apps 

`shinymisc` contains a number of apps that demonstrate different concepts.

To view an app, run the following:


```{r, eval=FALSE}
run_app(app_name = "theming")
```



* [Plot theming](https://github.com/Nelson-Gon/shinymisc/blob/main/R/theming.R)

This app takes a fairly advanced approach at demonstrating how one can combine different `shiny` principles to achieve plot customization. This was built to help me figure out how to best choose themes from different packages. In particular, I wanted to do this even if the package was not on the `search` list. 

This app explores concepts of reactivity, modularization, testing, and scaling 
in general. 

```{r, eval=FALSE}

run_app("theming")

```



* [Sample App](https://nelson-gon.shinyapps.io/sampleapp)

This app aims to do something fairly simple. It takes input data, allows user confirmation and finally prints the data entered. It was built as part of a blog I wrote to highlight `shiny` features like reactivity, observers, and performance improvements. This blog post is available at https://nelson-gon.github.io/12/12/2021/shiny-reactivity/. You can view the source code [here](https://github.com/Nelson-Gon/shinymisc/blob/main/R/sample_app.R).  

* [List Package Functions](https://github.com/Nelson-Gon/shinymisc/blob/main/R/list_functions.R)

This app was written as I tried to play around with namespaces and accessing functions in a package. In particular, I wanted to be able to load a function from a package without necessarily loading said package first. This is important because sometimes loading a package may result in function conflicts causing further debugging work.




Keep building,

Nelson 

`r Sys.Date()`


---

Please note that the `shinymisc` project is released with a [Contributor Code of Conduct](https://github.com/Nelson-Gon/shinymisc/blob/main/.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.



To raise an issue, please do so
[here](https://github.com/Nelson-Gon/shinymisc/issues)

Thank you, feedback is always welcome :)

